The role of emotional factors in face processing abilities in Autism Spectrum Conditions

### 2023-07-17 manuscript.Rmd
Added code snippet to the discussion

One limitation of the present study is that the non-autistic group showed surprisingly high levels of autistic and alexithymic traits. 46.9\% and 23.5\% of our “non-autistic” sample scored above threshold on the AQ and TAS-20 respectively (by comparison, 97.5\% and 52.5\% of the autistic group scored above threshold on these measures, which is in line with previous reports; @hoekstra2011a; @kinnaird2019a). While it suggests our non-autism sample may have been unusual in some way, our regression-based analyses should still have been able to uncover relationships between alexithymia, autistic traits and our face processing measures as there should still have been sufficient variation at the lower end of these scales for associations to be able to show themselves. Thus, we do not believe atypicalities in the non-autistic sample can account for the lack of effects.

>>>>

One limitation of the present study is that the non-autistic group showed surprisingly high levels of autistic and alexithymic traits. `r round(100*sum(TD$AQ>64)/length(TD$AQ),digits=1)`\% and `r round(100*sum(TD$TASTOTAL>60)/length(TD$TASTOTAL),digits=1)`\% of our “non-autistic” sample scored above threshold on the AQ and TAS-20 respectively (by comparison, 97.5\% and 52.5\% of the autistic group scored above threshold on these measures, which is in line with previous reports; @hoekstra2011a; @kinnaird2019a). While it suggests our non-autism sample may have been unusual in some way, our regression-based analyses should still have been able to uncover relationships between alexithymia, autistic traits and our face processing measures as there should still have been sufficient variation at the lower end of these scales for associations to be able to show themselves. Thus, we do not believe atypicalities in the non-autistic sample can account for the lack of effects.
